Hydra Battles and Cie

### 2021-07-20 doc/chapter-primrec.tex

\begin{Coqsrc}
Fail
  Fixpoint Ack (m n : nat) : nat :=
  match m, n with
  | 0, n => S n
  | S m, 0 => Ack m 1
  | S m0, S p => Ack m0 (Ack m p)
  end.
\end{Coqsrc}

\begin{Coqanswer}
The command has indeed failed with message:
Cannot guess decreasing argument of fix.
\end{Coqanswer}

@@

   Fixpoint Ack (m n : nat) : nat :=
     match m with
     | O => S n
     | S p => let fix Ackm (n : nat) :=
                  match n with
                  | O => Ack p 1
                  | S q => Ack p (Ackm q)
                  end
              in Ackm n
     end.

    Compute Ack 3 2.
\end{Coqsrc}

\begin{Coqanswer}
  = 29 : nat
\end{Coqanswer}

\begin{Coqsrc}
End Alt.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint Ack (m:nat) : nat -> nat :=
  match m with
  | 0 => S
  | S n => fun k =>  iterate (Ack n) (S k) 1
  end.

Compute Ack 3 2.
\end{Coqsrc}

\begin{Coqanswer}
  = 29 : nat
\end{Coqanswer}

>>>>

\input{movies/snippets/Ack/AckFixpointFail.tex}

@@

\input{movies/snippets/Ack/AckFixpointAlt.tex}

@@

\input{movies/snippets/Ack/AckFixpointIterate.tex}
